Characterizing the Splice Map of Turkey Hemorrhagic Enteritis Virus

### 2024-05-12 manuscript_thev_transcriptome.tex
all edits made prior to committee second edits after jvi submission

Characterizing the splice map of turkey hemorrhagic enteritis virus
(THEV) is an essential step that would allow studies of individual genes
mediating its immunosuppressive functions. We used RNA sequencing to
characterize the transcriptome of THEV for the first time, providing key
insights into the THEV gene expression and mRNA structures. Researchers
previously annotated the genome of THEV as encoding 23 open reading
frames (ORFs). In this work we identified 29 spliced transcripts all of
which contained novel exons although some exons matched some previously
annotated ORFs. The three annotated splice junctions were also
corroborated by our data. We performed PCR amplification of THEV cDNA,
cloned the PCR products, and used Sanger sequencing to validate all
identified splice junctions. During validation we identified five
additional unique transcripts, a subset of which were further validated
by 3' rapid amplification of cDNA ends (3' RACE) experiments. Thus, we
report that the genome of THEV contains 34 transcripts with the coding
capacity for all annotated ORFs. However, we found six of the previously
annotated ORFs (ORF1, E3, 33K, ORF8, IVa2, and protease) to be truncated
ORFs on the basis of the identification of an in-frame upstream start
codon or the detection of additional coding exons. We also identified
three of the annotated ORFs with longer or shorter isoforms, and seven
novel unannotated ORFs that could potentially be translated; although it
is beyond the scope of this manuscript to investigate whether they are
translated. Similar to other adenoviruses (AdVs), THEV also produces
multiple distinctly spliced transcripts that code for the same protein.
Our data show that all THEV transcripts are spliced and organized into
five transcription units under the control of their cognate promoters
like other AdVs. \newpage

\subsection{INTRODUCTION}\label{introduction}

@@

In summary, the THEV transcriptome bears remarkable similarity to the
better-studied MAdVs. The transcriptome is organized into five TUs, with
temporal regulation divided into early and late genes, and a broad
repertoire of transcripts are produced via virtually unlimited
alternative splicing. However, the THEV transcriptome appears less
sophisticated (i.e, it encodes fewer genes) than MAdVs, primarily
because the MAdV genomes are close to twice as long as that of THEV. The
lack of subdivision of the E1 region into E1a and E1b is one of the most
obvious examples. Also, the MAdV E4 region encodes several proteins
unlike in THEV where only one transcript encoding one protein was found.
The complexity of the MLTU leader sequences is another example. While
the majority of the THEV MLTU transcripts begin with the TPL just like
MAdVs with a small subset using a variant leader sequence (sTPL),
significantly more diverse 5'-UTRs are employed for MAdV MLTU
transcripts. Namely, the TPL, the so-called x, y, and z leaders, and the
i-leader are 5' leaders utilized by MAdV MLTU mRNAs. The absence of
these non-TPL leaders in our data could mean that the 5'-UTR diversity
of THEV's MLTU mRNAs is more limited due to its smaller genome size or
future studies using long read sequencing technologies could uncover
more variety not seen in our results. \newpage

@@

Sequencing reads were analyzed following a well-established protocol
described by Pertea \emph{et al} (25), using Snakemake - version 7.24.0
(33), a popular workflow management system to drive the pipeline.
Briefly, sequencing reads were trimmed with the Trim-galore - version
0.6.6 (34) program to achieve an overall Mean Sequence Quality (Phred
Score) of 36. Trimmed reads were mapped simultaneously to the complete
genomic sequence of avirulent turkey hemorrhagic enteritis virus
(\url{https://www.ncbi.nlm.nih.gov/nuccore/AY849321.1/}) and
\emph{Meleagris gallopavo}
(\url{https://www.ncbi.nlm.nih.gov/genome/?term=Meleagris+gallopavo})
using Hisat2 - version 2.2.1 (25) with default settings. The generated
binary alignment (BAM) files from each infection time point were
filtered for reads mapping to the THEV genome using Samtools - version
1.16.1 and fed into StringTie - version 2.2.1 (25) to assemble the
transcripts, using a gene transfer format (GTF) annotation file derived
from a gene feature format 3 (GFF3) annotation file obtained from NCBI,
which contains the predicted ORFs of THEV as a guide. GFFCOMPARE -
version 0.12.6 was used to merge all transcripts from all time points
without redundancy and using a custom R script, adenovirus transcripts
units (regions) were assigned to each transcript, generating the
transcriptome of THEV. StringTie was set to expression estimation mode
to calculate FPKM scores for all transcripts after which Ballgown -
version 2.33.0 in R was used to perform the statistical analysis on the
transcript expression levels. Samtools was also used to count the total
sequencing reads for all replicates at each time point and Regtools -
version 1.0.0 was used to count all junctions, the reads supporting
them, and extract all other information related to the junction. See
\textbf{Supplementary Computational Analysis} for the details of
transcript expression level estimations and splice junction read counts.

\subsubsection{DATA AVAILABILITY}\label{data-availability}

>>>>

\textbf{Background:} Hemorrhagic enteritis, caused by \emph{Turkey
Hemorrhagic Enteritis Virus (THEV)}, is a disease affecting turkey
poults characterized by immunosuppression and bloody diarrhea. An
avirulent THEV strain that retains the immunosuppressive ability is used
as a live vaccine. Characterizing the splice map of THEV is an essential
step that would allow studies of individual genes mediating its
immunosuppressive functions. We used RNA sequencing to characterize the
splice map of THEV for the first time, providing key insights into the
THEV gene expression and mRNA structures.\\
\textbf{Methods:} After infecting a turkey B-cell line with the vaccine
strain, samples in triplicates were collected at 4-, 12-, 24-, and
72-hours post-infection. Total RNA was extracted and poly-A-tailed mRNA
sequenced. Reads were mapped to the THEV genome after trimming and
transcripts assembled with StringTie. We performed PCR of THEV cDNA,
cloned the PCR products, and used Sanger sequencing to validate all
identified splice junctions.\\
\textbf{Results:} Researchers previously annotated the THEV genome as
encoding 23 open reading frames (ORFs). We identified 29 spliced
transcripts from our RNA sequencing data, all containing novel exons
although some exons matched some previously annotated ORFs. The three
annotated splice junctions were also corroborated by our data. During
validation we identified five additional unique transcripts, a subset of
which were further validated by 3' rapid amplification of cDNA ends (3'
RACE). Thus, we report that the genome of THEV contains 34 transcripts
with the coding capacity for all annotated ORFs. However, we found six
of the previously annotated ORFs to be truncated ORFs on the basis of
the identification of an in-frame upstream start codon or the detection
of additional coding exons. We also identified three of the annotated
ORFs with longer or shorter isoforms, and seven novel unannotated ORFs
that could potentially be translated; although it is beyond the scope of
this manuscript to investigate whether they are translated.\\
\textbf{Conclusions:} Similar to human adenoviruses, all THEV
transcripts are spliced and organized into five transcription units
under the control of their cognate promoters. The genes are expressed
under temporal regulation and THEV also produces multiple distinctly
spliced transcripts that code for the same protein.

\subsection{KEY WORDS}\label{key-words}

Alternative splicing, Turkey hemorrhagic enteritis virus, Adenovirus,
Transcriptome, RNA sequencing. \newpage

\subsection{BACKGROUND}\label{background}

@@

\subsection{CONCLUSIONS}\label{conclusions}

The THEV transcriptome bears remarkable similarity to the better-studied
MAdVs. The transcriptome is organized into five TUs, with temporal
regulation divided into early and late genes, and a broad repertoire of
transcripts are produced via virtually unlimited alternative splicing.
However, the THEV transcriptome appears less sophisticated (i.e, it
encodes fewer genes) than MAdVs, primarily because the MAdV genomes are
close to twice as long as that of THEV. The lack of subdivision of the
E1 region into E1a and E1b is one of the most obvious examples. Also,
the MAdV E4 region encodes several proteins unlike in THEV where only
one transcript encoding one protein was found. The complexity of the
MLTU leader sequences is another example. While the majority of the THEV
MLTU transcripts begin with the TPL just like MAdVs with a small subset
using a variant leader sequence (sTPL), significantly more diverse
5'-UTRs are employed for MAdV MLTU transcripts. Namely, the TPL, the
so-called x, y, and z leaders, and the i-leader are 5' leaders utilized
by MAdV MLTU mRNAs. The absence of these non-TPL leaders in our data
could mean that the 5'-UTR diversity of THEV's MLTU mRNAs is more
limited due to its smaller genome size or future studies could uncover
more variety not seen in our results. Being the first transcriptomic
characterization of THEV, this work should serve as useful resource to
future THEV gene expression and transcriptomic studies, especially,
mapping the mRNA splice sites. \newpage

@@

Sequencing reads were analyzed following a well-established protocol
described by Pertea \emph{et al} (25), using Snakemake - version 7.24.0
(33), a popular workflow management system to drive the pipeline.
Briefly, sequencing reads were trimmed with the Trim-galore - version
0.6.6 (34) program to achieve an overall Mean Sequence Quality (Phred
Score) of 36. Trimmed reads were mapped simultaneously to the complete
genomic sequence of avirulent turkey hemorrhagic enteritis virus
(\url{https://www.ncbi.nlm.nih.gov/nuccore/AY849321.1/}) and
\emph{Meleagris gallopavo}
(\url{https://www.ncbi.nlm.nih.gov/genome/?term=Meleagris+gallopavo})
using Hisat2 - version 2.2.1 (25) with default settings. The generated
binary alignment (BAM) files from each infection time point were
filtered for reads mapping to the THEV genome using Samtools - version
1.16.1 and fed into StringTie - version 2.2.1 (25) to assemble the
transcripts, using a gene transfer format (GTF) annotation file derived
from a gene feature format 3 (GFF3) annotation file obtained from NCBI,
which contains the predicted ORFs of THEV as a guide. GFFCOMPARE -
version 0.12.6 was used to merge all transcripts from all time points
without redundancy and using a custom R script, adenovirus transcripts
units (regions) were assigned to each transcript, generating the
transcriptome of THEV. StringTie was set to expression estimation mode
to calculate FPKM scores for all transcripts after which Ballgown -
version 2.33.0 in R was used to perform the statistical analysis on the
transcript expression levels. Samtools was also used to count the total
sequencing reads for all replicates at each time point and Regtools -
version 1.0.0 was used to count all junctions, the reads supporting
them, and extract all other information related to the junction. See
\textbf{Supplementary Computational Analysis} for the details of
transcript expression level estimations and splice junction read counts.
\newpage

\subsection{LIST OF ABBREVIATIONS}\label{list-of-abbreviations}

\begin{longtable}[c]{|p{1.00in}|p{2.00in}}

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Abbreviation}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Definition}}}} \\

\ascline{0.75pt}{666666}{1-2}\endfirsthead

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Abbreviation}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{\textbf{Definition}}}} \\

\ascline{0.75pt}{666666}{1-2}\endhead

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{AdV}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Adenovirus}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{MAdV}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Mastadenovirus}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{SiAdV}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Siadenovirus}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{THEV}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Turkey\ Hemorrhagic\ Enteritis\ Virus}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{HE}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Hemorrhagic\ Enteritis}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{UTR}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Untranslated\ Region}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TU}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Transcription\ Unit}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{L4P}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{L4\ Promoter}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{MLP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Major\ Late\ Promter}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{E3P}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{E3\ Promoter}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{hpi}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Hours\ Post-infection}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{qPCR}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Quantitative\ Polymerase\ Chain\ Reaction}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{FPKM}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Fragments\ Per\ Kilobase\ of\ transcript\ per\ Million\ mapped\ reads}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{CP}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Coding\ Potential}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TSS}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Transcription\ Start\ Site}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TTS}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Transcription\ Termination\ Site}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{SC}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Start\ Codon}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{STC}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Stop\ Codon}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{secSC}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Secondary\ Start\ Codon}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{secSTC}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Secondary\ Stop\ Codon}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{ORF}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Open\ Reading\ Frame}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{CDS}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Coding\ Sequence}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{MLTU}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Major\ Late\ Transcription\ Unit}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TPL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Tripartite\ Leader}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{sTPL}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Short\ Tripartite\ Leader}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{TPL3}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Third\ exon\ of\ Tripartite\ Leader}}} \\

\ascline{0.75pt}{666666}{1-2}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 1in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{GCN}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 0.75pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}!{\color[HTML]{666666}\vrule width 0.75pt}}{\textcolor[HTML]{000000}{\fontsize{10}{10}\selectfont{Genome\ Copy\ Number}}} \\

\ascline{0.75pt}{666666}{1-2}

\subsection{DATA AVAILABILITY}\label{data-availability}
